Brief Announcement: Tight Bounds for Online Balanced Repartitioning

### 2020-03-27 paper/paper.tex
On the learning problem

\section{The Learning Problem} %$\Omega(k\cdot \ell)$ for Competitive Ratio of Any Deterministic Algorithm}
\label{sec:lowerbound}

%In this section, we provide a lower bound $\Omega(k\cdot \ell)$ for the competitive ratio of any deterministic online algorithm.
%It is sufficient to have clusters of capacity $k\geq 3$ for this lower bound.
%For $k=2$ a constant competitive algorithm exists.
%At the end of this section, we also
%discuss an upper bound.

\noindent \textbf{Lower bound.}
The adversary constructs components of nodes based on the partitioning choices of a given online algorithm.
Adversary issues requests between pairs of nodes that belong to the same component.
If an online algorithm splits a component at any moment,
the adversary issues requests to the split pair until the algorithm collocates them.
We utilize the fact that the online algorithm does not know the components of the adversary, and it may split some components while evicting nodes.
On the other hand, $\OPT$ initially collocates all nodes of each component and never splits them again.

%\maciek{Here, we would like to introduce insights about the proof, emphasize the conditions for the bound to work (such as $k\geq 3$), and maybe compare to previously known lower bounds. Also, introduce the notation and definitions that are needed.}

@@

\noindent \textbf{Upper bound.}
Now we give an algorithm for a restricted variant of  \OBRP{}, named \PPOBRP{},
%\maciek{This is not sufficient! We also disallow serving requests remotely.}
where an optimal offline algorithm ($\OPT$) moves to a perfect partition
at the beginning and stays there perpetually.
%We refer this variant as \PPOBRP{}.
The task of an online algorithm for \PPOBRP{} is to recover (or learn) the perfect partition while not paying too much relative to \OPT.
%
%\maciek{This is not a valid description of the model. We need the assumption that collocation is needed in our model. Otherwise OPT would just serve some requests remotely, and our analysis would not hold.}
The first request between any two non-collocated nodes reveals an edge of the communication graph.
Our online algorithm collocates them immediately and never separates them since by assumption \OPT does the same.
Revealed edges, up to any point in the sequence,
induce some connected subgraphs which grow as components.
%An algorithm that always  keeps nodes belonging to the same component collocated is \emph{component respecting}.

>>>>

\section{The Learning Problem} %$\Omega(k\cdot \ell)$ for Competitive Ratio of Any Deterministic Algorithm}

\maciek{TODO: Intro to the learning problem is missing. What is the problem definition. How is it different from the general problem. Emphasize the fact that OPT is constrained not to migrate.}

\subsection{Lower bound.}

\label{sec:lowerbound}

In this section, we provide a lower bound $\Omega(k\cdot \ell)$ for the competitive ratio of any deterministic online algorithm.
It is sufficient to have clusters of capacity $k\geq 3$ for this lower bound.
For $k=2$ a constant competitive algorithm exists.
At the end of this section, we also
discuss an upper bound.

\maciek{TODO: better introduction of the concept of components IN THE LOWER BOUND. Perhaps other name than components to avoid confusion. Plus Figure.}

The adversary constructs components of nodes based on the partitioning choices of a given online algorithm.
Adversary issues requests between pairs of nodes that belong to the same component.
If an online algorithm splits a component at any moment,
the adversary issues requests to the split pair until the algorithm collocates them.
We utilize the fact that the online algorithm does not know the components of the adversary, and it may split some components while evicting nodes.
On the other hand, $\OPT$ initially collocates all nodes of each component and never splits them again.

\maciek{Here, we would like to introduce insights about the proof, emphasize the conditions for the bound to work (such as $k\geq 3$), and maybe compare to previously known lower bounds. Also, introduce the notation and definitions that are needed.}

@@

\maciek{Remark on resource augmentation. The lower bound for k=3 works even with significant augmentation (linear).}

\subsection{Upper bound.}
Now we give an algorithm for a restricted variant of  \OBRP{}, named \PPOBRP{},
%\maciek{This is not sufficient! We also disallow serving requests remotely.}
where an optimal offline algorithm ($\OPT$) moves to a perfect partition
at the beginning and stays there perpetually.
%We refer this variant as \PPOBRP{}.
The task of an online algorithm for \PPOBRP{} is to recover (or learn) the perfect partition while not paying too much relative to \OPT.
%
%\maciek{This is not a valid description of the model. We need the assumption that collocation is needed in our model. Otherwise OPT would just serve some requests remotely, and our analysis would not hold.}
The first request between any two non-collocated nodes reveals an edge of the communication graph.
Our online algorithm collocates them immediately and never separates them since by assumption \OPT does the same.
Revealed edges, up to any point in the sequence,
induce some connected subgraphs which grow as components.
%An algorithm that always  keeps nodes belonging to the same component collocated is \emph{component respecting}.
